The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-04-16 paper.qmd
updated some plots

# implicit 
ggplot(data_short, aes(x=x, y="X")) + geom_jitter() 
# explicit
ggplot(data_short, aes(x=x)) + geom_density()

# intrinsic
# avg data
avg_data <- data_long |> 
  group_by(name) |>
  summarise(mean = mean(value),
            sd = sd(value))
# plot
ggplot(avg_data, aes(x=mean, y=name, colour=sd)) +
  geom_point()

@@

# coincidence

# adjacent

>>>>

# implicit + visually integral
ggplot(data_short, aes(x=x, y="X")) + geom_jitter() 
# explicit
ggplot(data_short, aes(x=x)) + geom_density()

# intrinsic + separable
# avg data
avg_data <- data_long |> 
  group_by(name) |>
  summarise(mean = mean(value),
            sd = sd(value))
# plot
ggplot(avg_data, aes(x=mean, y=name, colour=sd)) +
  geom_point()

@@

# coincidence
## Basically all above plots

# adjacent
avg_data |>
  pivot_longer()
ggplot(avg_data, aes(x=mean, y=name, colour=sd)) +
  geom_point()
